Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-05 SupportingInformation.Rmd
adding allsp_pns_rchunk and other modifications

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
    toc: True
    includes:
      in_header: head_supp.sty

@@

<!--\tableofcontents-->
\listoftables
\listoffigures

\pagebreak

@@

@@

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf}
\caption[asym sensitivity results : copula plot]{asym sensitivity results : copula plot \label{fig_ms_asym_b_0.1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf}
\caption[asym sensitivity results : copula plot]{asym sensitivity results : copula plot \label{fig_ms_asym_b_0.9}}
\end{center}
\end{figure}

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
knitr::kable(summary_stat, booktabs = T, 
             format = "pandoc",
             digits=3,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asym. sensitivity \\label{tab_summary_stat_asym_sens}")
```

@@

```{r tab_stat_npa_asym_5,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[5]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[5]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_5}"))
```

\newpage
```{r tab_stat_npa_asym_6,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[6]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[6]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_6}"))
```

\newpage
```{r tab_stat_npa_asym_7,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[7]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[7]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_7}"))
```

```{r tab_stat_npa_asym_8,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[8]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[8]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_8}"))
```

# Cause of non-Normal copula structure : Asymmetric sensitivity and copula structure in populations \label{Cause_asym_sens}

To test the assymetric sensitivity, we constructed a two habitat patch model for population $P_{i} (i=1,2)$ as follows;

\begin{equation}\label{eq.AS}
P_{i}(t+1) = b P_{i}(t) + g(\epsilon_{i}(t)) + h(\delta_{i}(t))
\end{equation}

$b$ was the linear growth rate. Global environmental fluctuation function $g(\epsilon)$ can take up any one form between $g_{1}$ and $g_{2}$ (Eq. \ref{eq.AS_g}) where $\epsilon=(\epsilon_{1}, \epsilon_{2})$ was an iid through time with mean zero and covariance matrix $\Sigma_{\epsilon}$.

\begin{align}
g(\epsilon) = \begin{cases} 
g_{1} = \begin{cases}
\epsilon & \text{if $\epsilon< 0$}; \\
0 & \text{otherwise}.
\end{cases}\\ \\
g_{2} = \begin{cases}
\epsilon & \text{if $\epsilon> 0$}; \\
0 & \text{otherwise}\label{eq.AS_g}.
\end{cases}
\end{cases} \text{where } \epsilon = N(\textbf{0},\Sigma_{\epsilon})\;\ \text{with} \;\ \Sigma_{\epsilon} = \begin{bmatrix} 1 & r \\ r & 1 \end{bmatrix}
\end{align}

Local environmental fluctuation function $h(\delta)$ varied according to Eq. \ref{eq.AS_h} where $a$ was the scaling parameter between $0$ to $1$. $\delta=(\delta_{1}, \delta_{2})$ was an iid across $i=(1,2)$ and time with mean zero and covariance matrix $\Sigma_{\delta}$.

\begin{equation}\label{eq.AS_h}
h(\delta) = a \delta = aN(\textbf{0},\Sigma_{\delta})\;\ \text{with} \;\ \Sigma_{\delta} = \begin{bmatrix} 1 & 0 \\ 0 & 1 \end{bmatrix}
\end{equation}

We simulated our model (\ref{eq.AS}) for different values of $b$ with $a=0.2$, $r=0.8$. $10000$ points were generated from each local and global fluctuations to apply on the initial populations and then after simulation we kept only last $1000$ time step of simulated points to plot the population-copula for a specific $b$ and a specific functional form of $g$  (For code see [`Simulator_asym_sens`](https://github.com/sghosh89/BIVAN/blob/master/asym_sensitivity.R) function). Fig. \ref{fig_ms_asym_b_0.1} and Fig. \ref{fig_ms_asym_b_0.9} show these results for $b=\pm0.1$ and $b=\pm0.9$, respectively. We also carried out model selection and non-parametric statistical analysis with each copula of those figures and summarized our results in Tables \ref{tab_summary_stat_asym_sens} - \ref{tab_stat_npa_asym_8}. Table \ref{tab_summary_stat_asym_sens} represent the model selection results with AIC weights for best fitted copula and normal copula, model averaged lower and upper tail dependence, p-values (both Cramer-von Mises statistic and Kolmogorov-Smirnov statistic) for goodness of fit test. In each case, successful bootstrap was $100\%$. According to our model selection approach, for $b=\pm0.1$, non-normal copula (with higher AIC weights) were always best-fit with some asymetric tail dependence whereas for $b\pm0.9$, most of the time normal was best. It is probably because the populations get long-time exposure to environmental changes for slower growth(or decay) rate and so global fluctuation can affect them more efficiently. Our non-parametric analysis results (Tables \ref{tab_stat_npa_asym_1} -\ref{tab_stat_npa_asym_8}) are consistent with this model selection approach.

@@

\begin{figure}[!h]
\textbf{ \hspace{6 cm} (A) \hspace{6 cm} (B)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6 cm} (C) \hspace{6 cm} (D)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf}
\caption{Skewness of spatially averaged $(A)$ green-spruce aphid's abundance, $(B)$ leaf-curling plum aphid's firstflight date, $(C)$ ceratium furca's abundance and $(D)$ methane-flux data, were indicated by red line in each plot and were compared with respect to skewness of spatially averaged 10000 Normal surrogates preserving Spearman correlation). \label{fig_skewness_spearman}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.1 cm} (D)} \\
\vspace{-0.5 cm} 
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.pdf}\\
\end{center}
\textbf{ \hspace{2.8 cm} (E) \hspace{1.8 cm} (F) \hspace{1.8 cm} (G) \hspace{1.8 cm} (H) \hspace{1.6 cm} (I) \hspace{2 cm} (J)}\\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_7stats_spearman.pdf}
\caption[Spatial Taylor's Law results]{Spatial Taylor's Law results: log(spatial variance) vs. log(spatial mean) for $ns=10$ number of (A) Clayton, (B) Normal, (C) Frank, (D) Survival Clayton surrogates; (E) p-value for test of linearity, (F) p-value for test of homoskedasticity, (G) root mean square error, (H) intercept, (I) slope, (J) quadratic coefficient of regression line for first panel plot. \label{fig_spTL}}
\end{center}
\end{figure}

>>>>

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: head_supp.sty

@@

\pagenumbering{roman}
\tableofcontents
\listoftables
\listoffigures

\pagebreak
\pagenumbering{arabic}

@@

```{r modelsel_and_npa_pns_allsp, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("NonParamStat.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

set.seed(seed)
library(parallel)
source("FittingCopula_selective_loc.R")
RES_all_sp_pns<-mclapply(X=c(1:22),FUN=RES_single_sp,d_allsp=data_plankton_north_sea,
                              families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=45,
                              good_loc_given=F,good_loc=NA,mc.cores=3)
saveRDS(RES_all_sp_pns,"./Results/fitting_results/RES_all_sp_pns.RDS")

source("good_loclist.R")
source("NonParamStat.R")
resloc<-"./Results/stat_results/stat_plankton_north_sea/"

stat_plankton_north_sea_allsp<-vector("list",22)

for(sp in 1:22){
  nm<-paste("sp_",sp,sep="")
  resloc2<-paste(resloc,nm,sep="")
   if (!dir.exists(resloc2)){
    dir.create(resloc2)
  }
  good_loc<-good_loclist(d_allsp=data_plankton_north_sea,sp=sp,data_pt_thrs=45)

  temp<-multcall(d_allsp=data_plankton_north_sea,sp=sp,lats=lats,longs=longs,
                                      pfname=paste(resloc2,"/","Sp_",sp,sep=''),good_loc=good_loc)
  stat_plankton_north_sea_allsp[[sp]]<-temp
}
saveRDS(stat_plankton_north_sea_allsp,paste(resloc,file="stat_plankton_north_sea_allsp.RDS",sep=''))

summary_pns_allsp<-as.data.frame(matrix(NA,nrow=22,ncol=8))
colnames(summary_pns_allsp)<-c("species","#LTmUT>0","#LTmUT<0","val_LTmUT>0","val_LTmUT<0",
                                     "CorlmCoru_mean_CI","PlmPu_mean_CI","D2umD2l_mean_CI")

for(sp in c(1:22)){
  #cat("sp=",sp,"\n")
  summary_pns_allsp$species[sp]<-sp
  LTmUT<-(RES_all_sp_pns[[sp]]$LTdep_AICw - RES_all_sp_pns[[sp]]$UTdep_AICw) 
  summary_pns_allsp$`#LTmUT>0`[sp]<-sum(LTmUT>0,na.rm=T)
  summary_pns_allsp$`#LTmUT<0`[sp]<-sum(LTmUT<0,na.rm=T)
  ind_LTmUT_pos<-which(LTmUT>0,arr.ind = T)
  summary_pns_allsp$`val_LTmUT>0`[sp]<-sum(LTmUT[ind_LTmUT_pos])
  ind_LTmUT_neg<-which(LTmUT<0,arr.ind = T)
  summary_pns_allsp$`val_LTmUT<0`[sp]<-sum(LTmUT[ind_LTmUT_neg])

  summary_pns_allsp$CorlmCoru_mean_CI[sp]<-list(
    c(unname(round(stat_plankton_north_sea_allsp[[sp]]$numericdf[9,c(2:4)],3))))
  summary_pns_allsp$PlmPu_mean_CI[sp]<-list(
    c(unname(round(stat_plankton_north_sea_allsp[[sp]]$numericdf[10,c(2:4)],3))))
  summary_pns_allsp$D2umD2l_mean_CI[sp]<-list(
    c(unname(round(stat_plankton_north_sea_allsp[[sp]]$numericdf[11,c(2:4)],3))))
}
saveRDS(summary_pns_allsp,"./Results/summary_pns_allsp.RDS")
```

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/SClayton_kendall.pdf}
\caption[Comparing correlations and non-parametric statistic between noise-copula (\textbf{Survival Clayton}) and population copula for different \textbf{Kendall's Tau}]{Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from \textbf{Survival Clayton} copula and of the affected populations for 9 equidistant \textbf{Kendall's Tau} values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison) \label{fig_Cause4copula_SC_kend}}
\end{center}
\end{figure}

@@

<!--
\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf}
\caption[asym sensitivity results : copula plot]{asym sensitivity results : copula plot \label{fig_ms_asym_b_0.9}}
\end{center}
\end{figure}-->

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
knitr::kable(summary_stat[,c(1:4)], booktabs = T, 
             format = "pandoc",
             digits=3,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asym. sensitivity \\label{tab_summary_stat_asym_sens}")
```

@@

<!--
```{r tab_stat_npa_asym_5,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[5]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[5]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_5}"))
```

```{r tab_stat_npa_asym_6,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[6]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[6]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_6}"))
```

```{r tab_stat_npa_asym_7,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[7]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[7]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_7}"))
```

```{r tab_stat_npa_asym_8,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[8]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[8]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_8}"))
```
-->
<!--
# Cause of non-Normal copula structure : Asymmetric sensitivity and copula structure in populations \label{Cause_asym_sens}
-->

@@

\begin{figure}[!h]
\textbf{ \hspace{6 cm} (A) \hspace{6 cm} (B)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_kendall.pdf}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_kendall.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6 cm} (C) \hspace{6 cm} (D)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_kendall.pdf}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_methane/skewness_methane_kendall.pdf}
\caption{Skewness of spatially averaged $(A)$ Green-spruce aphid's abundance, $(B)$ Leaf-plum curling aphid's firstflight date, $(C)$ Ceratium furca's abundance and $(D)$ methane-flux data, were indicated by red dot in each plot and were compared with respect to skewness of spatially averaged 10000 Normal surrogates preserving Kendall correlation). \label{fig_skewness_kendall}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{2.8 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.6 cm} (D)} \\
\vspace{-0.5 cm} 
\begin{center}
\includegraphics[width=18 cm]{./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.pdf}\\
\end{center}
\textbf{ \hspace{1.8 cm} (E) \hspace{1.6 cm} (F) \hspace{1.8 cm} (G) \hspace{1.8 cm} (H) \hspace{1.8 cm} (I) \hspace{1.8 cm} (J) \hspace{1.8 cm} (K)}\\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=18 cm]{./Results/taylorslaw_results/SpatialTL_7stats_spearman.pdf}
\caption[Spatial Taylor's Law results]{Spatial Taylor's Law results: log(spatial variance) vs. log(spatial mean) for $ns=10$ number of (A) Clayton, (B) Normal, (C) Frank, (D) Survival Clayton surrogates; (E) p-value for test of linearity, (F) p-value for test of homoskedasticity, (G) root mean square error, (H) intercept, (I) slope, (J) quadratic coefficient, (K) mean curvature of regression line from first panel-plots. \label{fig_spTL}}
\end{center}
\end{figure}

```{r spatialTL_on_realdata_aphid_count, results="hide", echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("TaylorsLawTools.R"),mtime("mncurvat.R"),mtime("ncsurrog.R"))}

set.seed(seed)
source("ncsurrog.R")
source("TaylorsLawTools.R")
source("good_loclist.R")

TL_on_realdata<-function(data,numsurrog=1000,sp,data_pt_thrs,ploton,tag,labelon=T){

  loclist<-good_loclist(d_allsp=data,sp=sp,data_pt_thrs=data_pt_thrs)
  data<-data[[sp]]
  df<-c()
  for(i in loclist){
    tem<-data[[i]]$Dat
    df<-cbind(df,tem)
  }
  colnames(df)<-paste("loc",loclist,sep="")
  df<-na.omit(df)

  mat_real<-as.matrix(df)
  check_rep<-function(y){all( abs(y - mean(y)) < 1e-8 )} #This fn checks for repeatation of same values in a vector
  call_check_rep<-apply(mat_real,1,check_rep) # checks the same for mat_real matrix along all row

  if(all(call_check_rep==F)==T){

    realTL_stats<-tl_stats(m = mat_real)
    real_spatialTLslope<-unname(realTL_stats$s.stats[5])
    real_sTL_quadcoeff<-unname(realTL_stats$s.stats[6])
    real_sTL_mncurv<-unname(realTL_stats$s.stats[7])

    #generate the normal surrogates with spearman correlation preserving
    array_surrog<-ncsurrog(m=mat_real,corpres="spearman",numsurrog=numsurrog)

    bad_id<-c()
    for(i in 1:numsurrog){
      m<-array_surrog[,,i]
      mean_m<-apply(X=m, MARGIN = 1, FUN = mean)
      var_m<-apply(X=m, MARGIN = 1, FUN = var)
      if(any(mean_m==0) | any(var_m==0)){
        bad_id<-c(bad_id,i)
      }
    }

    m<-array_surrog
    if(length(bad_id)!=0){
      m<-array_surrog[,,-bad_id]
    }
    ts<-apply(m,3,tl_stats)

    good_surrog_slope<-c()
    good_surrog_quadcoeff<-c()
    good_surrog_mncurv<-c()
    for(i in c(1:length(ts))){
      good_surrog_slope<-c(good_surrog_slope,unname(ts[[i]]$s.stats[5]))
      good_surrog_quadcoeff<-c(good_surrog_quadcoeff,unname(ts[[i]]$s.stats[6]))
      good_surrog_mncurv<-c(good_surrog_mncurv,unname(ts[[i]]$s.stats[7]))
    }

    numsurrog_good<- numsurrog - length(bad_id)

    p_left<-sum(good_surrog_slope < real_spatialTLslope)/numsurrog_good
    p_right<-sum(good_surrog_slope > real_spatialTLslope)/numsurrog_good

    p_left_quadcoeff<-sum(good_surrog_quadcoeff < real_sTL_quadcoeff)/numsurrog_good
    p_right_quadcoeff<-sum(good_surrog_quadcoeff > real_sTL_quadcoeff)/numsurrog_good

    p_left_mncurv<-sum(good_surrog_mncurv < real_sTL_mncurv)/numsurrog_good
    p_right_mncurv<-sum(good_surrog_mncurv > real_sTL_mncurv)/numsurrog_good

    if(ploton==T & tag=="slope"){
      hist(good_surrog_slope,breaks=100,main="",xlab="surrogate_TL_slope",cex.axis=1.5,cex.lab=1.5)
      points(x=real_spatialTLslope,y=0,col="red",pch=15)
      if(labelon==T){
        mtext(paste0("sp= ",sp,", p_left= ",round(p_left,3),", p_right=",round(p_right,3),sep=""),
              side = 3, line=-2, adj=0, col="blue")
      }
    }

    if(ploton==T & tag=="quadcoeff"){
      hist(good_surrog_quadcoeff,breaks=100,main="",xlab="surrogate_TL_quadcoeff",cex.axis=1.5,cex.lab=1.5)
      points(x=real_sTL_quadcoeff,y=0,col="red",pch=15)
      if(labelon==T){
        mtext(paste0("sp= ",sp,", p_left= ",round(p_left_quadcoeff,3),", p_right=",round(p_right_quadcoeff,3),sep=""),
              side = 3, line=-2, adj=0, col="blue")
      }
    }

    if(ploton==T & tag=="mncurv"){
      hist(good_surrog_mncurv,breaks=100,main="",xlab="surrogate_TL_meanCurvature",cex.axis=1.5,cex.lab=1.5)
      points(x=real_sTL_mncurv,y=0,col="red",pch=15)
      if(labelon==T){
        mtext(paste0("sp= ",sp,", p_left= ",round(p_left_mncurv,3),", p_right=",round(p_right_mncurv,3),sep=""),
              side = 3, line=-2, adj=0, col="blue")
      }
    }

  }else{
    real_spatialTLslope<-NA
    p_left<-NA
    p_right<-NA
    numsurrog_good<-NA
    real_sTL_quadcoeff<-NA
    p_left_quadcoeff<-NA
    p_right_quadcoeff<-NA
    real_sTL_mncurv<-NA
    p_left_mncurv<-NA
    p_right_mncurv<-NA
  }
  return(list(realTL_stats=realTL_stats,
              real_spatialTLslope=real_spatialTLslope,
              p_left=p_left,
              p_right=p_right,
              numsurrog_good=numsurrog_good,
              real_sTL_quadcoeff=real_sTL_quadcoeff,
              p_left_quadcoeff=p_left_quadcoeff,
              p_right_quadcoeff=p_right_quadcoeff,
              real_sTL_mncurv=real_sTL_mncurv,
              p_left_mncurv=p_left_mncurv,
              p_right_mncurv=p_right_mncurv,
              surrogTL_stats=ts,
              good_surrog_mncurv=good_surrog_mncurv))
}

#call on real data
# For all sp
splist<-c(1:20)
tl_aphid_count<-as.data.frame(matrix(NA,nrow=length(splist),ncol=10))
colnames(tl_aphid_count)<-c("real_sTL_slope","p_left","p_right","numsurrog_good",
                            "real_sTL_quadcoeff","p_left_quadcoeff","p_right_quadcoeff",
                            "real_sTL_mncurv","p_left_mncurv","p_right_mncurv")
rownames(tl_aphid_count)<-paste("sp",splist,sep="")
#pdf("aphid_count_allsp_spTLslope.pdf",height=20,width=20)
#pdf("./Results/taylorslaw_results/aphid_count_allsp_sTL_quadcoeff.pdf",height=20,width=20)
pdf("./Results/taylorslaw_results/aphid_count_allsp_sTL_mncurv.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
for(i in splist){
  #cat("sp=",i,"\n")
  #ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=i,data_pt_thrs = 30,ploton=T,tag="slope",labelon=T)
  #ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=i,data_pt_thrs = 30,ploton=T,tag="quadcoeff",labelon=T)
  ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=i,data_pt_thrs = 30,ploton=T,tag="mncurv",labelon=T)
  tl_aphid_count$real_sTL_slope[i]<-ans$real_spatialTLslope
  tl_aphid_count$p_left[i]<-ans$p_left
  tl_aphid_count$p_right[i]<-ans$p_right
  tl_aphid_count$numsurrog_good[i]<-ans$numsurrog_good
  tl_aphid_count$real_sTL_quadcoeff[i]<-ans$real_sTL_quadcoeff
  tl_aphid_count$p_left_quadcoeff[i]<-ans$p_left_quadcoeff
  tl_aphid_count$p_right_quadcoeff[i]<-ans$p_right_quadcoeff
  tl_aphid_count$real_sTL_mncurv[i]<-ans$real_sTL_mncurv
  tl_aphid_count$p_left_mncurv[i]<-ans$p_left_mncurv
  tl_aphid_count$p_right_mncurv[i]<-ans$p_right_mncurv
}
par(op)
dev.off()
saveRDS(tl_aphid_count,"./Results/taylorslaw_results/tl_aphid_count.RDS")
```

```{r spatialTL_on_realdata_aphid_count_sp6, results="hide", echo=F, cache=T, cache.extra=list(seed,data_aphid_count,TL_on_realdata,mtime("good_loclist.R"),mtime("TaylorsLawTools.R"),mtime("mncurvat.R"),mtime("ncsurrog.R"))}

set.seed(seed)

#Now for sp=6
sp<-6
pdf("./Results/taylorslaw_results/aphid_count_sp6_sTL_mncurv.pdf",height=5,width=5)
ans<-TL_on_realdata(data=data_aphid_count,numsurrog=10000,sp=sp,data_pt_thrs = 30,ploton=T,tag="mncurv",labelon = F)
mtext(paste0("p= ",round(ans$p_left_mncurv,3)),side = 3, line=-2, adj=0.5, col="blue")
dev.off()

pdf("./Results/taylorslaw_results/aphid_count_sp6_logv_vs_logm.pdf",height=5,width=10)
op<-op<-par(mfrow=c(1,2),mar=c(4,5,1,1),mgp=c(3,1,0))
plot(ans$realTL_stats$s.points,xlab=expression(log[10]("spatial mean")),
     ylab=expression(log[10]("spatial variance")),col="red",
     cex.axis=1.5,cex.lab=1.5)
mtext(paste0("mean curvature= ",round(unname(ans$realTL_stats$s.stats[7]),3)),side = 3, line=-2, adj=0.5, col="blue")

target_mncurv<-0.1
id<-which(abs(ans$good_surrog_mncurv-target_mncurv)<1e-4)[1]
ans_s<-ans$surrogTL_stats
plot(ans_s[[id]]$s.points,xlab=expression(log[10]("spatial mean")),
     ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)
mtext(paste0("mean curvature= ",round(ans$good_surrog_mncurv[id],3)),side = 3, line=-2, adj=0.5, col="blue")
